---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
load("~/Documents/izzy work/BRFSS2022_rev.RData")
```
```{r}
library(ggplot2)
library(tidyverse)
```
```{r}
# first want to make some factors into numbers
brfss22$Age_midpt <- fct_recode(brfss22$X_AGEG5YR, "21" = "Age 18 to 24",
                                      "27" = "Age 25 to 29", "32" = "Age 30 to 34",
                                      "37" = "Age 35 to 39", "42" = "Age 40 to 44",
                                      "47" = "Age 45 to 49", "52" = "Age 50 to 54",
                                      "57" = "Age 55 to 59", "62" = "Age 60 to 64",
                                      "67" = "Age 65 to 69", "72" = "Age 70 to 74",
                                      "77" = "Age 75 to 79", "82" = "Age 80 or older",
                                      NULL = "Dont know/Refused/Missing")
brfss22$Age_midpt <- as.numeric(levels(brfss22$Age_midpt))[brfss22$Age_midpt]
brfss22$income_midpoint <- fct_recode(brfss22$INCOME3, 
                        "7500" = "Household income less than $10,000",
                        "12500" = "Less than $15,000 ($10,000 to less than $15,000)",
                        "17500" = "Less than $20,000 ($15,000 to less than $20,000) ",
                        "22500" = "Less than $25,000 ($20,000 to less than $25,000) ",
                        "30000" = "Less than $35,000 ($25,000 to less than $35,000) ",
                        "42500" = "Less than $50,000 ($35,000 to less than $50,000) ",
                        "62500" = "Less than $75,000 ($50,000 to less than $75,000)",
                        "87500" = "Less than $100,000 ($75,000 to less than $100,000)",
                        "125000" = "Less than $150,000 ($100,000 to less than $150,000)",
                        "175000" = "Less than $200,000 ($150,000 to less than $200,000)",
                        "210000" = "$200,000 or more",
                        NULL = "Dont know/Not sure",
                        NULL = "Refused")
brfss22$income_midpoint <- as.numeric(levels(brfss22$income_midpoint))[brfss22$income_midpoint]

brfss22$Educ_number <- fct_recode(brfss22$EDUCA, 
                                  "0" = "Never attended school or only kindergarten", 
                                  "4.5" = "Grades 1 through 8 (Elementary)",
                                  "10" = "Grades 9 through 11 (Some high school)",
                                  "12" = "Grade 12 or GED (High school graduate)",
                                  "14" = "College 1 year to 3 years (Some college or technical school)",
                                  "16" = "College 4 years or more (College graduate)",
                                  NULL = "Refused" )
brfss22$Educ_number <- as.numeric(levels(brfss22$Educ_number))[brfss22$Educ_number]

# this level name can create problems later so fix it here
levels(brfss_marijan$X_PRACE2)[7] <- "dont know not sure"

select1 <- !is.na(brfss22$MARIJAN1)
brfss_marijan <- subset(brfss22, select1 )


p_cannabis_age <- ggplot(data = brfss_marijan,
                       mapping = aes(x = Age_midpt,
                                     y = MARIJAN1))
p_cannabis_age + geom_smooth()
```

```{r}
model_1 <- lm(MARIJAN1 ~ Age_midpt, data = brfss_marijan)
summary(model_1)
```
```{r}
model_2 <- lm(MARIJAN1 ~ Age_midpt + X_PRACE2 + X_HISPANC + EDUCA, data = brfss_marijan)
summary(model_2)
```

# maybe get fancy
require(stargazer)
stargazer(model_2, type = "text")
# play with stargazer instead of summary, it can look nicer!
# it might throw an error at top but then work fine, just ignore it
```
```{r}
model_2 <- lm(MARIJAN1 ~ Age_midpt + X_PRACE2 + X_HISPANC + EDUCA, data = brfss_marijan)
summary(model_2)

# maybe get fancy
require(stargazer)
stargazer(model_2, type = "text")
# play with stargazer instead of summary, it can look nicer!
# it might throw an error at top but then work fine, just ignore it
```
```{r}
brfss22$GENHLTH_RECODE <- fct_recode(brfss22$GENHLTH,
                                  "0" = "Poor",
                                  "1" = "Fair",
                                  "2" = "Good",
                                  "3" = "Very Good",
                                  "4" = "Excellent",
                                  NULL = "Refused",
                              NULL = "Dont know - Not Sure")

brfss22$GENHLTH_RECODE <-  as.numeric(levels(brfss22$GENHLTH_RECODE))[brfss22$GENHLTH_RECODE]
```
```{r}
brfss22$VETERAN3 <- fct_recode(brfss22$VETERAN3,
                               "0" = "No",
                               "1" = "Yes a veteran")
brfss22$VETERAN3 <- as.numeric(levels(brfss22$VETERAN3))[brfss22$VETERAN3]
```
```{r}
model_2 <- lm(MARIJAN1 ~ Age_midpt + X_PRACE2 + X_HISPANC + EDUCA, data = brfss_marijan)
summary(model_2)

model_3 <- lm(MARIJAN1 ~ Age_midpt + I(Age_midpt^2) + X_PRACE2 + X_HISPANC + EDUCA, data = brfss_marijan)
summary(model_3)
```
```{r}
to_be_predicted_2 <- data.frame(Age_midpt = 25:55, X_PRACE2 = "Black or African American",
                          X_HISPANC = "no", EDUCA = "Grade 12 or GED (High school graduate)")

to_be_predicted_2$yhat <- predict(model_2, newdata = to_be_predicted_2)
```
```{r}
to_be_predicted_2$yhat3 <- predict(model_3, newdata = to_be_predicted_2)
to_be_predicted_2$yhat4 <- predict(model_4, newdata = to_be_predicted_2)


d_for_graphing <- data.frame(Age_midpt = 25:55, 
                             to_be_predicted_2$yhat,
                             to_be_predicted_2$yhat3,
                             to_be_predicted_2$yhat4)

p_predvals <- ggplot(d_for_graphing, aes(Age_midpt))
p_predvals + geom_line(aes(y = to_be_predicted_2.yhat)) + 
  geom_line(aes(y = to_be_predicted_2.yhat3), color = 'blue') +
  geom_line(aes(y = to_be_predicted_2.yhat4), color = 'red')
```
```{r}
quantile(brfss_marijan$MARIJAN1, probs = c(0.99,0.95,0.94,0.93,0.92,0.91,0.9))

# or convert to a factor to see the counts
brfss_marijan$MARIJAN_factor <- as.factor(brfss_marijan$MARIJAN1)
summary(brfss_marijan$MARIJAN_factor)
```
```{r}
brfss_marijan$Marijan_01 <- as.numeric(brfss_marijan$MARIJAN1 > 0)
# do a summary to check that it looks right

model_5 <- lm(Marijan_01 ~ Age_midpt*(X_PRACE2 + X_HISPANC) + I(Age_midpt^2)*(X_PRACE2 + X_HISPANC) + X_PRACE2 + X_HISPANC + EDUCA, data = brfss_marijan)
summarymodel_5)
```
```{r}
HW 6
My group members are Chris Lacroix and Rosairi Estevez
 The research that I picked is Ruglass, Espinosa, etv al (2020). This research focuses on college students' cannabis use motives. Important factor is that data was collected from three universities with different cannabis legislation. Profile differences were assessed such as regulatory environment, alcohol use, negative affect, social context of use, negative consequences and cannabis use. Six profiles emerged and differed in alcohol use, social context of use, regulatory environment, and negative affect. Participants with high and multiple motives had excessive cannabis use and negative consequences compared to profiles with low and fewer motives. Participants that indicated high avoidance motives had a greater cannabis use and consequences. This study can use the Brfss data by analyzing factors such as cannabis use, age, and adverse child experiences . Most motives for cannabis use comes from child experiences especially if cannabis was used by parents or anyone near the child. We could check what age students started using cannabis, what kind of adverse child experiences they had was it substance abuse, domestic abuse, and sexual abuse.  We can graph this data and see whether there are any correlation or what other factors we can input to better the data

```
